Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-10 doc/peakcharacterization_manuscript.Rmd
new manuscript with better sized figure

```{r get_setup}
source("./packages.R")
lapply(list.files("./R", full.names = TRUE), source)

@@

```{r mz_frequency_conversion, dn_id = figure_count}
tar_load(frequency_conversion)
frequency_conversion$all
```

>>>>

```{r get_setup, include = FALSE}
source("./packages.R")
lapply(list.files("./R", full.names = TRUE), source)

@@

```{r mz_frequency_conversion, dn_id = figure_count, fig.width = 16, fig.height = 10}
tar_load(frequency_conversion)
frequency_conversion$all
```
